Characterization of integrated crop-livestock-forest system in Brazil

### 2022-07-25 iclfs_review/lit_review.qmd
Create literature review document using Quarto.

---
title: The aspects of integrated crop-livestock-forest system in Brazil

author: Hugo Tameirão Seixas

output:
  html_document:
    theme: readable
    number_sections: true

---

# Title and Abstract

# Aims and questions

## Provide a rationale for the review

## Reference any previous reviews or meta-analyses on the topic

## State the aims and scope of the review (including its generality)

@@

## State the primary questions the review addresses (e.g. which moderators were tested)

## Describe whether effect sizes were derived from experimental and/or observational comparisons

# Review registration

# Eligibility criteria

# Finding studies

## Define the type of search (e.g.comprehensive search, representative sample)

## State what sources of information were sought (e.g. published and unpublished studies, personal communications)

## Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators

@@

## Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates)

# Study selection

# Data collection process

# Data items

# Assessment of individual study quality

# Effect size measures

# Missing data

# Meta-analytic model description

# Software

# Non independence

# Meta-regression and model selection

# Publication bias and sesitivity analysis

# Clarification of post hoc analysis

# Metadata data and code

# Results of study selection process

# Sample sizes and study characteristics

# Meta-analysis

# Heterogeneity

# Meta-regression

# Outcomes of publication bias and sensitivity analyses

# Discussion

# Contributions and funding

# References

>>>>

---
title: "Characterization of integrated crop-livestock-forest system in Brazil"
author: "Hugo Tameirão Seixas"
format: 
  html:
    page-layout: article
editor: visual
---

## Title and Abstract

## Aims and questions

### Provide a rationale for the review

### Reference any previous reviews or meta-analyses on the topic

### State the aims and scope of the review (including its generality)

@@

### State the primary questions the review addresses (e.g. which moderators were tested)

### Describe whether effect sizes were derived from experimental and/or observational comparisons

## Review registration

## Eligibility criteria

## Finding studies

### Define the type of search (e.g.comprehensive search, representative sample)

### State what sources of information were sought (e.g. published and unpublished studies, personal communications)

### Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators

@@

### Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates)

## Study selection

## Data collection process

## Data items

## Assessment of individual study quality

## Effect size measures

## Missing data

## Meta-analytic model description

## Software

## Non independence

## Meta-regression and model selection

## Publication bias and sesitivity analysis

## Clarification of post hoc analysis

## Metadata data and code

## Results of study selection process

## Sample sizes and study characteristics

## Meta-analysis

## Heterogeneity

## Meta-regression

## Outcomes of publication bias and sensitivity analyses

## Discussion

## Contributions and funding

## References
